\documentclass{tccv}
\usepackage[english,croatian]{babel}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
% TODO fix think of new better design, maybe change font

\begin{document}

%\part{Filip Marić}
\part
    [hr.linkedin.com/in/filipmrc]
    %{Frouedova 7\newline 10000, Zagreb, Croatia}
    {+385 98 904 9565}   
    {filipmaric@protonmail.com}
    {15.04.1993, Zagreb, Croatia} 
 
       
\section{Work experience} 
 
\begin{eventlist}
  
\item{Jan. 2018 - Present} 
     {\textit{Graduate researcher @} \textbf{\href{http://www.starslab.ca/}{STARS} Laboratory}}
     %{}   
     
     Researching applications of tools from computational algebraic geometry for manipulator kinematics, control, synthesis and motion planning. 

\item{Oct. 2018 - Apr. 2019} 
     {\textit{Subject matter expert @} \textbf{Coursera}}  
     %{Subject matter expert}

     Developing assignments and materials for the Coursera \href{https://www.coursera.org/learn/state-estimation-localization-self-driving-cars}{state estimation specialization}.

\item{Jul. 2016 -- Aug. 2016}    
     {\textit{R\&D intern @} \textbf{Institute for Nuclear Technology}}
     %{Research and development intern}
     
Designing framework for computer vision algorithms used in robot manipulator localization. Developing in C\# with OpenCV libraries and utilizing structural properties of nuclear plant.
 
%\item{September 2014 -- January 2015}
%     {Human Oriented Technologies Laboratory} 
%     {Software tester}   
%       
%Testing video facial expression analysis software.
%Providing feedback and design suggestions.
\end{eventlist}

\section{Publications}
\begin{yearlist2}
\item{}   
     {{\small \href{https://arxiv.org/abs/1909.09318}{arxiv.org/abs/1909.09318} \textit{@} ICRA 2020}}
     {{\small Inverse Kinematics for Serial Kinematic Chains via Sum of Squares Optimization}}

\item{}
     {{\small \href{https://arxiv.org/abs/1908.02963}{arxiv.org/abs/1908.02963} \textit{@} IROS 2019}}
     {{\small Fast Manipulability Maximization Using Continuous-Time Trajectory Optimization}} 
     
\item{}
     {{\small \href{https://arxiv.org/abs/1803.06406}{arxiv.org/abs/1803.06406} \textit{@} ICRA 2018}}
     {{\small Self-Calibration of Mobile Manipulator Kinematic and Sensor Extrinsic Parameters Through Contact-Based Interaction}}

     \item{}
     {{\small \href{https://ieeexplore.ieee.org/document/7522303}{10.1109/MIPRO.2016.7522303} \textit{@} MIPRO 2016}}
     { Robot arm teleoperation via RGBD sensor palm tracking - \href{https://youtu.be/exf7TUviuSg}{video}}
%\item{2015}
 %    {National Exporters Convention}
  %   {Programming robotic arm for central role in award ceremony.
   %    \href{http://goo.gl/U6IJrW}{Giving out trophies} to industry leaders with the robotic arm semi-autonomously.}
\end{yearlist2}
\vspace*{-0.5cm}
%
\section{Awards and Achievements}
\begin{yearlist}
\item[University of Toronto]{2018}
     {UofT Joint Educational Placement}
     {{\small Fully funded international PhD collaboration with the \href{https://lamor.fer.hr/}{LAMoR} laboratory at the UZagreb.}}
     
\item[University of Zagreb]{2017}
     {Dr. Jasna Šimunić-Hrvoić scholarship}
     {{\small Full financing for working on my Master's thesis at the University of Toronto.}}

\item[University of Zagreb]{2016}
     {Rectors award}
     {{\small Awarded for best student scientific \href{https://www.dropbox.com/s/k66438qy0xz13c4/rektorova.pdf?dl=0}{thesis}.}}

%\item[eStudent]{2016}
%     {Elektroboj 2016}
%     {{\small Secured funding for the KER project, proceeded to win 3rd place in the competition.}}
     
\item[European Comission]{2015}
     {Erasmus scholarship}
     {\begin{small}
     Exchange scholarship awarded based on academic results.
     \end{small}}
\end{yearlist}

\section{Education}
%%\small{Faculty Of Electrical Engineering and Computing (FER)}
\begin{yearlist}
\item[University of Toronto]{now}
     {Ph.D candidate, Robotics}
     {{\small Space and Terrestrial Autonomous Robotics Systems (STARS) Laboratory }}
\item[University of Zagreb]{2017}
     {M.Sc, Electrical Engineering and IT}
     {{\small Laboratory for Autonomous Systems and Mobile Robotics (LAMoR)}}
\item[University of Toronto]{2017} 
     {Graduate exchange}
     {{\small Institute for Aerospace Studies}}
\item[Aalborg Universitat]{2016}
     {Graduate exchange}
     {{\small Department of Electronic Systems}}
\end{yearlist}
\vspace*{-0.5cm}
%
\section{Projects \& Other}
\begin{yearlist2}
\item{}
     {\small Thing mobile manipulator}
     {{\small Developing motion planning and control for the \href{https://youtu.be/l_MliB_B_UQ}{Thing} mobile manipulator at STARS Laboratory.}}
     
\item{}
     {\small Haptic feedback for the DaVinci surgical robot} 
     {{\small Developing haptic feedback for minimally invasive surgery with DaVinci surgical robot and Geomagic touch haptic controller.}}

     \item{}
     {\small Kinematic Educational Robot (KER)}
     {{\small \href{https://github.com/filipmrc/ker}{Open source}, low-cost quadruped platform with ROS and simulation capabilities.}}
\end{yearlist2}
\vspace*{-0.5cm}
%
\section{Software skills}
\begin{factlist}

\item{Experienced}
     {MATLAB, ROS, Simulink, Gazebo}

\item{Intermediate}
     {C++, Python, Git, Blender, Linux} %step 7

\item{Basic}
     {PCL, AutoCAD, ZMQ, emacs}
\end{factlist}
\vspace*{-0.5cm} 
%
\section{Engineering skills}
\begin{factlist}
\item{Experienced}
	 {Robotics, Control, Motion Planning}
	 
\item{Intermediate}
     {Estimation theory, Optimization}
    
\item{Basic}
     {Microcontrollers, Machine learning} 
\end{factlist}
\vspace*{-0.5cm}
%
\section{Language skills}
\begin{factlist}
\item{English}{Full professional proficiency \\ (TOEFL: 109/120)}
\item{French}{Elementary proficiency} 
\item{Croatian}{Native speaker}
\end{factlist}
\vspace*{-0.5cm}
%
\section{Other experience}
\begin{factlist}
\item{ }{Leading and working in large and small international teams}
\item{ }{Presenting projects at international conventions, for reporters, investors}
\end{factlist}

\end{document} 
 
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
